Honors Thesis Proposal

### 2009-04-12 honors_thesis/proposal/paper.tex
Started working on a preliminary thesis for English 316.  Will be changed a lot for the actual thesis.

In running experiments, many trials will be run and averaged, as there is a
random component in this algorithm.  I will use statistical tests for all
comparisons to the original PSO algorithm.  The success criterion will be a
better performance of the algorithm as measured by the lowest function
evaluation seen over a number of function evaluations for several benchmark and
real-world problems.  Speculative execution requires more function evaluations 
per particle than a na\"ive parallel PSO, %TODO
PSO with the same number of particles, so the two algorithms will be compared
at points where they use equal amounts of function evaluations per iteration.

>>>>

In running experiments, many trials will be run and averaged, as there is a
random component in this algorithm.  I will use statistical tests for all
comparisons to the original PSO algorithm.  The success criterion will be a
better performance of the algorithm as measured by the lowest function
evaluation seen over a number of function evaluations for several benchmark and
real-world problems.  Performing speculative execution in PSO requires more
function evaluations per particle than regular PSO, so to be fair the two
algorithms will be compared with configurations where each uses the same number
of functions evaluations per iteration, not the same number of particles.
